---
title: "Verbose Grob Output"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Verbose Grob Output}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(grid)
library(ingrid)
```


# `{grid}` is not very verbose

The `grid::print.grob()` method is quite terse, and only prints the type
of grob and its name.

```{r}
cg <- circleGrob(x = 0.5, y = 0.5, r = unit(10, 'mm'), default.units = 'npc')
cg
```


# `{ingrid}` offers verbose grob output

A user can request that the grob print methods from print are replaced with 
ones from `ingrid`.

By calling `ingrid::register_verbose_printing()` then new verbose methods 
are used for the following:

* `print.grob()`
* `print.polyclipgrob()`
* `print.gtree()`
    * Will verbosely print the nested grobs within a tree
* `print.gpar()`
* `print.viewport()`

```{r}
ingrid::register_verbose_printing()
cg
```


Call `deregister_verbose_printing()` if this verbosity is no longer required.





















